\section{Acknowledgments} 
The author extends profound gratitude to the luminaries who have paved the way for this exploration, both those alive and those whose legacy endures. This work stands on the shoulders of giants such as Sir Roger Penrose, Stuart Hameroff, Dimitri Nanopoulos, and Nick Mavromatos, whose pioneering theories laid the groundwork for the integration of quantum mechanics and biology. Special acknowledgment is also given to the critics and skeptics like Max Tegmark, whose challenges inspired the pursuit of more rigorous and testable frameworks. 
\subsection{Conflicts of Interest} 
The author declares no conflicts of interest. Although previously employed by Gilead Sciences, Inc. and previously a shareholder, this affiliation has NO bearing on the representation or interpretation of the reported results.  
\subsection{Ethical AI use and Transparency} 
The author also acknowledges the significant contributions of artificial intelligence tools, including OpenAI ChatGPT, JetBrains IDE AI, and Overleaf Editor AI, for model validation, code refinement, and manuscript preparation. These tools improved the clarity, rigor, and accessibility of the work, ensuring a high standard of academic integrity. A bidirectional research collaboration was established, with routine bias audits and verification of all AI-assisted content.
Gratitude is extended to the open source development community for foundational tools such as the NumPy, Matplotlib, and Python libraries, without which this research would not have been possible. 
These contributions remind us of the collective effort that drives scientific discovery. 
\subsection{Author Contributions} 
ACD conceptualized, designed, guided, analyzed, visualized, wrote, and edited all aspects of this publication. The author acknowledges the collaborative role of AI in literature searches, model validation, simulation debugging, and enhancing the readability of the manuscript. All final decisions, interpretations, and conclusions were made by the author. 
\subsection{Funding} 
This research did not receive external funding. 
\subsection{Institutional Review} 
This study is entirely computational and did not involve human or animal participants, which required IRB approval. 